\pdfbookmark[section]{Abstract}{toc}
\begin{abstract}

  \gls{jfnk} methods promise a robust framework for solving nonlinear equations.
  The \gls{jfnk} methods converge $q$-quadratically and only require a finite
  difference Jacobian-vector product rather than a full Jacobian.  However, the
  adoption of the \gls{jfnk} method in the simulation of nuclear reactors has
  proven difficult due to computational complexity. As such, the traditional
  \gls{pi} method is typically preferred to solve for the fundamental eigenmode
  of a nuclear reactor system.

  In \citetitle{qe2paper}, authors \citeauthor{qe2paper} present an
  implementation of the \gls{jfnk} method to solve the \gls{nem} equations. In
  their implementation, the authors reduce the number of solution variables by
  employing local-elimination and improve the efficiency of the Krylov solver by
  preconditioning with a specially designed, physics-based, preconditioner. This
  implementation of the \gls{jfnk} method is compared to a \gls{pi} method and
  the authors conclude that ``the \gls{nem}\_\gls{jfnk} methods can greatly
  improve the convergence rate and the computational efficiency''
  \cite{qe2paper}.
  
  The claims by the authors are exaggerated and insufficient results are
  provided to justify such claims. The claim of improved computational
  efficiency is based on comparing the proposed \gls{jfnk} method to a
  suboptimal implementation of the \gls{pi} method. Notably, the authors do not
  properly consider the importance of the \gls{ws} and do not use a \gls{cmfd}
  formulation of the \gls{nem} equations. In their closing remarks,
  \citeauthor{qe2paper} also claim that the proposed methods can be extended to
  multiphysics simulations though other work suggests this is challenging, if at
  all feasible \cite{caslJFNK}.

  Ultimately, \citeauthor{qe2paper} present a comparison of suboptimal codes and
  suggest that the \gls{jfnk} method is preferable because it had reduced
  execution time. Such claims cannot be substantiated by the results presented.
  It is essential to compare optimized codes before making conclusions regarding
  an improvement in methods.

\end{abstract}
\glsresetall
